Order is half of life -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-30 paper/paper-mainfile.tex
some changes
change title

\title{Ordering is half the battle -- Establishing Totally Ordered HTN
	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}

@@

\begin{table} 
	\centering  
	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule
		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
		\midrule
		SmartPhone  & 4.0                   &  1     \\
		Transport   & 1144.9                & 40       \\
		UM-Translog & 1.1                    & 17   \\
		Woodworking & 2035              &   21    \\
				\bottomrule 
	\end{tabular} 
	}
\end{table}

@@

While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
\begin{table} 
	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain. Shows Results for Both Inference Methods.}\label{} 
	\begin{tabular}{lccl} 
		\toprule 
		Domain & Complex & Simple &  \\ 
		\midrule
		Transport & 1.0 & 0.0  \\ 
		UM-Translog & 0.8 & 0.0  \\ 
		Satellite & 1.0 & 0.0  \\ 
		Monroe Fully Observ. & 1.0 & 0.0  \\ 
		Rover & 1.0 & 0.0  \\ 
		Woodworking & 0.9 & 0.0  \\ 
		Monroe Part. Observ. & 1.0 & 0.0  \\ 
		PCP & 0.0 & 0.0  \\ 
		Barman-BDI & 1.0 & 0.0  \\ 
		SmartPhone & 0.1 & 0.1  \\ 
		Monroe & 0.8 & 0.0  \\ 
		Zenotravel & 1.0 & 0.0  \\ 
		\bottomrule 
	\end{tabular} 
\end{table}

>>>>

\title{Order is half of life -- Establishing Totally Ordered HTN
	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}

@@

\begin{table} 
	\centering  
	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
	\label{table:FullyLinearizedProblems}
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule
		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
		\midrule
		SmartPhone  & 4.0                   &  1     \\
		Transport   & 1144.9                & 40       \\
		UM-Translog & 1.1                    & 17   \\
		Woodworking & 2035              &   21    \\
				\bottomrule 
	\end{tabular} 
	}
\end{table}

@@

While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)

\begin{table} 
	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain. Shows Results for Both Inference Methods.}\label{table:POMethodBreak} 
	\begin{tabular}{lccl} 
		\toprule 
		Domain & Complex & Simple &  \\ 
		\midrule
		Transport & 1.0 & 0.0  \\ 
		UM-Translog & 0.8 & 0.0  \\ 
		Satellite & 1.0 & 0.0  \\ 
		Monroe Fully Observ. & 1.0 & 0.0  \\ 
		Rover & 1.0 & 0.0  \\ 
		Woodworking & 0.9 & 0.0  \\ 
		Monroe Part. Observ. & 1.0 & 0.0  \\ 
		PCP & 0.0 & 0.0  \\ 
		Barman-BDI & 1.0 & 0.0  \\ 
		SmartPhone & 0.1 & 0.1  \\ 
		Monroe & 0.8 & 0.0  \\ 
		Zenotravel & 1.0 & 0.0  \\ 
		\bottomrule 
	\end{tabular} 
\end{table}
